Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments

### 2019-07-13 paper.tex
More references

Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal\todo{cite voice appers}, audio\todo{cite audio papers} and haptic\todo{cite haptic} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with vision impairments report that they prefer haptic and vocal feedback out of the 3 options. 
However, haptic feedback systems require significant additional hardware to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions. 
Simple audio tones do not suffer from these bandwidth and hardware limitations as badly, but it does have the potential to fatigue the user's senses if the tone is too harsh, psychologically speaking.

@@

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous research results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.37}{\radian} and \SI{0.51}{\radian} for groups \textit{G1} and \textit{G2} respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 46\% and 26\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a lesser improvement (11\%) with \textit{G1} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization} and a 18\% reduction in performance for group \textit{G2}.
However, the participants from~\cite{stanley2006lateralization} all had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for group \textit{G2} is centered around the negative angle, indicating a possible underlying bias in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization} and warrants an investigation with a larger participant pool to determine the underlying bias, if any.

>>>>

Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with vision impairments report that they prefer haptic and vocal feedback out of the 3 options. 
However, haptic feedback systems require significant additional hardware to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions. 
Simple audio tones do not suffer from these bandwidth and hardware limitations as badly, but it does have the potential to fatigue the user's senses if the tone is too harsh, psychologically speaking.

@@

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous research results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.37}{\radian} and \SI{0.51}{\radian} for groups \textit{G1} and \textit{G2} respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 46\% and 26\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a lesser improvement (11\%) with \textit{G1} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization} and a 18\% reduction in performance for group \textit{G2}.
However, the participants from~\cite{stanley2006lateralization} all had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for group \textit{G2} are centred around the negative angle, indicating a possible underlying bias in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization} and warrants an investigation with a larger participant pool to determine the underlying bias, if any.
